Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-26 ms.tex
FP table updates
numbers changed

\newcommand{\Nfp}{4}
\newcommand{\Nvalidated}{22} %16 without contrast curves
\newcommand{\Nlimbo}{10} %adds up to 36

@@

Such a scheme enables us to infer the statistical uncertainties on the
mass, radius, and effective temperature.
However, we are subject to biases induced by systematics in the models themselves.
There is some evidence that the Dartmouth models may under-predict
radii of M dwarfs by $\sim 15\%$ when compared to other methods \citep{Newton15,
Montet15}.
Such an effect may be the result of the Dartmouth model reliance on BT-Settl
atmospheres, which have been shown to predict near-IR colors that are too blue
\citep{Thompson14}.

In order to account for the effects of model uncertainties, we also run
MCMC chains with photometric errors inflated artificially by a factor of three.
We provide full chains using both inflated and un-inflated
uncertainties,\footnote{\url{http://www.astro.princeton.edu/~tdm/k2/}}
though in the rest of this work (and in Table 2) we adopt
the results obtained using the inflated values.

\subsection{SpeX Spectroscopy}
\label{Spexobs}

@@

As has been well known from the early days of transit searches, it is
possible for an eclipsing binary star to masquerade as a transiting
planet if (a) it is a highly grazing eclipse, or (b) the binary system
shares a photometric aperture with a significantly brighter star, 
resulting in a diluted eclipse depth.
When possible, such astrophsycial false positive scenarios are traditionally
ruled out by detailed follow-up observations, often a combination of
high-resolution imaging and radial-velocity measurements.
However, the \kep\ mission, with its thousands of planet candidates
around mostly faint stars, necessitated a paradigm shift---a move
toward probabilistic interpretation of transit signals, rather than
comprehensive follow-up of each individual candidate \citep{Morton11b}.

@@

We note that we validate 201828749 as a true transiting planet, despite the presence of this binary
companion.
From the transit shape, we can rule out the possibility this system is a background eclipsing
binary.
Regardless of which star this object transits, the object is planet-sized.
Given that small planets are significantly more common than large planets, it is more likely
that the planet is orbiting the brighter star, and our parameters listed in Table 3 reflect this
likelihood. If the planet is truly orbiting the fainter star, then it has a larger radius than is
listed in this table.

@@

The two observed spectra have RVs that differ by $47 \pm 42$ m s$^{-1}$.
If the RVs were caused by a stellar companion, the RV shift between these
observations would be on the order of km s$^{-1}$.
Therefore, the transiting object must be planetary in nature.

@@

\subsection{Two Candidates, One Ephemeris}

>>>>

\newcommand{\Nfp}{5}
\newcommand{\Nvalidated}{13} 
\newcommand{\Nrecandidate}{7}
\newcommand{\Nlimbo}{11} %adds up to 36

@@

Such a scheme enables us to infer the statistical uncertainties on the
mass, radius, and effective temperature.
However, we are subject to biases induced by systematics in the models themselves.
There is some evidence that the Dartmouth models may under-predict
radii of M dwarfs by $\sim 15\%$ when compared to other methods \citep{Newton15,
Montet15}.
Such an effect may be the result of the Dartmouth model reliance on BT-Settl
atmospheres, which are based on incomplete molecular line lists and
have been shown to predict near-IR colors that are too blue
\citep{Thompson14}.

In order to account for the effects of model uncertainties, we also run
MCMC chains with photometric errors inflated artificially by a factor of three.
The observed photometric parameters are then consistent with spectroscopically-derived
parameters for stars with published spectra, and consistent with typical uncertainties
from photometric data \citep[e.g.][]{Huber14}.
We provide full chains using both inflated and un-inflated
uncertainties,\footnote{\url{http://www.astro.princeton.edu/~tdm/k2/}}
though in the rest of this work (and in Table 2) we adopt
the results obtained using the inflated values.

\subsection{SNIFS and SpeX Spectroscopy}
\label{Spexobs}

@@

As has been well known from the early days of transit searches, it is
possible for an eclipsing binary star to masquerade as a transiting
planet. 
There are many scenarios which can cause an astrophysical false positive.
The most common scenarios are if (a) it is a highly grazing eclipse, or (b) the binary system
shares a photometric aperture with a significantly brighter star, 
resulting in a diluted eclipse depth.
When possible, such astrophsycial false positive scenarios are traditionally
ruled out by detailed follow-up observations, often a combination of
high-resolution imaging and radial-velocity measurements.
However, the \kep\ mission, with its thousands of planet candidates
around mostly faint stars, necessitated a paradigm shift---a move
toward probabilistic interpretation of transit signals, rather than
comprehensive follow-up of each individual candidate \citep{Morton11b}.

@@

We note that we validate 201828749 as a true transiting planet, despite the presence of this binary
companion.
From the transit shape, we can rule out the possibility this system is a background eclipsing
binary.
Regardless of which star this object transits, the object is planet-sized.
In Table 3, we assume the planet is orbiting the larger star. 
If the planet is truly orbiting the fainter star, then its radius must be larger than is listed to 
account for the observed transit depth.

@@

The two observed spectra have RVs that differ by $47 \pm 42$ m s$^{-1}$.
If the RVs were caused by a stellar companion, the RV shift between these
observations would be on the order of km s$^{-1}$.
Therefore, we can rule out any stellar-mass companions that would be able
to create this transit signal.

@@

\subsection{Two Candidates, One Ephemeris}
\label{sec:ephemmatch}
